Convective penetration probably parameterizes convective overshoot

### 2021-07-10 manuscript/ms.tex
two-column-ified things and updates to MESA section

% Preamble
\documentclass{aastex631}
\usepackage{natbib}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{epstopdf}
\usepackage{hyperref}

@@

\begin{abstract}
Convection is a crucial heat transport and dynamical excitation mechanism in stars.
Parameterizations like mixing length theory adequately describe bulk convective flows, but the behavior of convective motions near convective boundaries are not well understood.
In this paper we examine how convective motions mix the background thermodynamic profiles and in turn extend the size of the convection zone, a process referred to as convective penetration.
We use a simplified Boussinesq model of stellar convection with a radiative flux.
We derive a ``penetration parameter'' $\mathcal{P}$ which compares how drastically the radiative gradient deviates from the adiabatic gradient on either side of the convective boundary.
Following \citet{roxburgh1989} and \citet{zahn1991}, we derive a parameterization in which the size of the convection zone is set by $\mP$ and the energy dissipation.
We perform 3D numerical simulations using Dedalus and find good agreement with this theory.
In stellar contexts, we expect $\mathcal{P} \approx 1$ and in this regime our results suggest that convection zones may extend beyond the Schwarzschild boundary by some 20-30\% of a mixing length.
We present a MESA solar model which uses our parameterization of convective penetration, and find that the base of the solar convection zone extends by (X amount for some choice of parameters).
We briefly discuss future experiments which could verify and extend these results to stellar contexts.
\end{abstract}
\keywords{UAT keywords}

@@

The mechanisms referred to as ``convective overshoot'' in the stellar literature fall into two hydrodynamical classes.
The first class is, confusingly, also called ``\emph{convective overshoot}'' in the fluid dynamics literature and refers to motions which extend beyond the convective boundary and mix chemical compositions but importantly do not adjust the thermodynamic profile.
The second class is called ``\emph{convective penetration},'' and refers to convective motions which mix the thermodynamic profiles beyond the convective boundary, thereby extending the adiabatically-mixed convective region.
We will follow a deep history \citep{zahn1991, brummell_etal_2002, korre_etal_2019} and use this terminology; the primary focus of this work is convective penetration.

@@

\subsection{Kinetic energy \& the dissipation-flux link}
\label{sec:theory_energy}
\begin{figure}[t!]
\centering
\includegraphics[width=\textwidth]{theory_profiles.pdf}
\caption{
(left) The vertical profile of the kinetic energy fluxes $\mathcal{F}$.
This profile goes to zero at the bottom boundary, again at the dashed line, and at the top of the PZ near $z \approx 1.5$; Eqn.~\ref{eqn:integral_constraint} holds between any two of these points.
(middle) the evolved value of $\justgrad$ (green) compared to $\gradad$ (grey) and $\gradrad$ (red); note the extended penetration zone where $\justgrad \approx \gradad > \gradrad$.
(right) Source terms from Eqn.~\ref{eqn:kinetic_energy_1D} normalized by the maximum of $\overline{\mathcal{B}}$.
\label{fig:theory_profiles}
}
\end{figure}

@@

We now find it instructive to break up the convecting region into a classical ``convection zone'' (CZ) and a extended ``penetration zone'' (PZ); we will assume that convective motions are efficient in each of these zones so that $\justgrad = \gradad$ in both the CZ and PZ.
We furthermore note that the buoyant energy generation is directly proportional to the convective flux, $\bar{\mathcal{B}} = |\alpha|g\bar{w T'} = |\alpha| g \bar{\Fconv}$.
Thus, in the PZ where $\gradad > \gradrad$, we know that $\bar{\Fconv} < 0$ and so $\bar{\mathcal{B}} < 0$ too (see the discussion around Eqn.~\ref{eqn:gradrad_definition}).
Breaking up Eqn.~\ref{eqn:integral_constraint}, we see that
\begin{equation}
\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz \qquad=\qquad
\int_{\rm{CZ}} \bar{\Phi}\,dz + \int_{\rm{PZ}} \bar{\Phi}\,dz + \int_{\rm{PZ}}(-\bar{\mathcal{B}})\,dz.
\label{eqn:constraint_cz_pz_split}
\end{equation}
Eqn.~\ref{eqn:constraint_cz_pz_split} is thus arranged so that the (positive) buoyant engine of convection is on the left-hand side, and the (positive) sinks of work are on the RHS.
We see that the size of the PZ is set by some combination of viscous dissipation and buoyancy breaking.
We now parameterize the fraction of the buoyant engine consumed by CZ dissipation  
\begin{equation}
f \equiv \frac{\int_{\rm{CZ}} \bar{\Phi}\,dz}{\int_{\rm{CZ}}\bar{\mathcal{B}}\,dz}.
\label{eqn:f_defn}
\end{equation}
Under this parameterization, Eqn.~\ref{eqn:constraint_cz_pz_split} can be written
\begin{equation}
\frac{\int_{\rm{PZ}} \bar{\Phi}\,dz + \int_{\rm{PZ}}(-\bar{\mathcal{B}})\,dz}{\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz}
= 1 - f,
\label{eqn:first_pz_parameterization}
\end{equation}
and we can immediately read off limits on a hypothetical PZ according to $f$,
\begin{enumerate}
\item In the limit that $f \rightarrow 0$, viscous dissipation is extremely inefficient.
It is probably also reasonable to assume that $\int_{\rm{PZ}}\bar{\Phi}\,dz \rightarrow 0$, and so Eqn.~\ref{eqn:first_pz_parameterization} states that the PZ must be large enough for its negative buoyant work to be equal in magnitude to the positive buoyant work of the CZ.
This is the integral constraint on the maximum size of the PZ that \citet{roxburgh1989} derived.
\item In the limit that $f \rightarrow 1$, viscous dissipation is efficient in the CZ and cancels out the work done by buoyancy.
This is the case in standard Rayleigh-B\'{e}nard convection when the convection is contained between two hard plates.
Per Eqn.~\ref{eqn:first_pz_parameterization}, the positive-definite PZ terms must approach zero and no PZ develops in this limit.
\end{enumerate}
In general, we anticipate from the results of e.g., \citet{currie_browning_2017} that $f$ is closer to 1 than 0, but its precise value must be measured directly from simulations.
Indeed, we find that $f \gg 0$ but $f < 1$ in our simulations (see e.g., Fig.~\ref{fig:theory_profiles}, right panel).

Assuming that a PZ of depth $\delp$ develops above a CZ of depth $L_{\rm{CZ}}$, we model the PZ dissipation as
\begin{equation}
\int_{\rm{PZ}} \bar{\Phi}\,dz = \xi\frac{\delp}{L_{\rm{CZ}}}\int_{\rm{CZ}}\bar{\Phi} = \xi \delp \Phi_{\rm{CZ}}.
\label{eqn:xi_defn}
\end{equation}
Here $\Phi_{\rm{CZ}}$ is the average dissipation value in the CZ and $\xi$ is a parameter that describes the shape of the dissipation profile as a function of height in the PZ.
In other words, we assume that $\bar{\Phi} \approx \Phi_{\rm{CZ}}$ at the CZ-PZ boundary and then falls off with height.
The shape of $\bar{\Phi}$ determines the value of $\xi$, with a linear falloff producing $\xi = 1/2$, a quadratic falloff producing $\xi = 2/3$, and if $\bar{\Phi}$ does not decline with height then $\xi = 1$.
Regardless, $\xi$ is another measurable parameter bounded by $[0, 1]$. 
With this parameterization, we rewrite Eqn.~\ref{eqn:first_pz_parameterization}
\begin{equation}
-\frac{\int_{\rm{PZ}}\bar{\Fconv}\,dz}{\int_{\rm{CZ}}\bar{\Fconv}\,dz} + f\xi\frac{\delp}{L_{\rm{CZ}}}
= (1 - f).
\label{eqn:theory_fraction}
\end{equation}
In order to derive a specific prediction for the PZ depth, it is necessary to specify the vertical shape of $\overline{\Fconv}$.
We will study two cases in this work, laid out below.
In both of these cases, we will define a nondimensional ``Penetration Parameter'' whose magnitude is set by the ratio of the convective flux some equidistant length $\epsilon$ both above and below the Schwarzschild convective boundary $L_s$ (assuming the region above the boundary is an adiabatic penetrative zone),
\begin{equation}
\mP \equiv -\frac{\overline{\Fconv}(z = L_s - \epsilon)}{\overline{\Fconv}(z = L_s + \epsilon)}.
\label{eqn:theory_P_defn}
\end{equation}
Since $\Fconv < 0$ in the PZ, the sign of $\mP$ is positive.
Intuitively, $\mP$ describes which terms are important in Eqn.~\ref{eqn:first_pz_parameterization}.
When $\mP \ll 1$, the buoyancy term dominates in the PZ and dissipation can be neglected there.
When $\mP \gg 1$, buoyancy is negligible in the PZ and dissipation constrains the size of the PZ.
When $\mP \sim 1$, both terms matter.

@@

\section{Simulation Details}
We nondimensionalize Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq} on the length scale of the Schwarzschild-unstable convection zone $L_s$, the timescale of freefall across that convection zone $\tau_{\rm{ff}}$, and the temperature scale of the internal heating over that freefall time $\Delta T$,
\begin{equation}
\begin{split}
&T^* = (\Delta T)T = Q_0 \tau_{\rm{ff}} T,\qquad
\partial_{t^*} = \tau_{\rm{ff}}^{-1}\partial_t = \left(\frac{|\alpha| g Q_0}{L_s}\right)^{1/3} \partial_t,\qquad
\grad^* = L_s^{-1} \grad,\qquad
\vec{u}^* = u_{\rm{ff}}\vec{u} = \left(|\alpha| g Q_0 L_s^2\right)^{1/3}\vec{u},
\\
&p^* = \rho_0 u_{\rm{ff}}^2\varpi,\qquad
k^* = (L_s^2 \tau_{\rm{ff}}^{-1})k,\qquad
Q^* = Q_0 Q,\qquad
\mR = \frac{u_{\rm{ff}} L_s}{\nu},\qquad
\Pran = \frac{\nu}{\chi}.
\end{split}
\end{equation}
For convenience, here we define quantities with $*$ (e.g., $T^*$) as being the ``dimensionful'' quantities of Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq}.
Going forward, quantities without $*$ (e.g., $T$) will be dimensionless.
The dimensionless equations of motion are therefore
\label{sec:simulation_details}
\begin{align}
&\grad\dot\vec{u} = 0 
\label{eqn:nondim_incompressible} \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\grad \varpi + T \hat{z} + \mR^{-1}\grad^2 \vec{u}
\label{eqn:nondim_momentum} \\
&\partial_t T + \vec{u}\dot\grad T + w \grad_{\rm{ad}}  + \grad\dot[-k \grad \overline{T}] = (\Pran\mR)^{-1}\grad^2 T' + Q.
\label{eqn:nondim_temperature}
\end{align}
We construct a domain in the range $z \in [0, L_z]$ where in this work we choose $L_z \geq 2$ so that the domain is at least twice as deep as the Schwarzschild-unstable convection zone.
We decompose the temperature field into a time-stationary initial background and fluctuations, $T(x, y, z, t) = T_0(z) + T_1(x, y, z, t)$.
For boundary conditions, we impose impenetrable, no-slip boundary conditions at the top and bottom of the box so that $\vec{u} = 0$ at $z = [0, L_z]$.
We also impose a fixed-flux boundary at the bottom of the box ($\partial_z T_1 = 0$ at $z = 0$) and a fixed temperature boundary at the top of the domain ($T_1 = 0$ at $z = L_z$).
For a select few simulations, we impose stress-free instead of no-slip boundary conditions ($w = 0$ and $\partial_z u = \partial_z v = 0$ at $z = [0, L_z]$).

@@

\subsection{Case I: Discontinuous flux}
Most of the simulations in this paper have a discontinuous convective flux at the Schwarzschild convective boundary.
We achieve this by constructing a discontinuous radiative conductivity,
\begin{equation}
k = \begin{cases}
k_{\rm{CZ}}	&	z < 1 \\
k_{\rm{RZ}} &	z \geq 1
\end{cases},
\label{eqn:sim_discontinuous_k}
\end{equation}
where CZ refers to the convection zone and RZ refers to the radiative zone (some of which will be occupied by the penetrative zone PZ).
Leaving $\mS$ and $\mP_D$ as free parameters and requiring that the adiabatic gradient can carry $\Fbot$ at $z = 0$ and that the radiative gradient can carry $F_H + \Fbot$ for $z \geq 1$ specifies this system fully,
\begin{equation}
k_{\rm{RZ}} = \frac{\delta_H}{\mS\mP_D},\qquad
k_{\rm{CZ}} = k_{\rm{RZ}}\frac{1}{1 + \zeta + \mP_D^{-1}},\qquad
\gradad = Q_{\rm{mag}}\mS\mP_D(1 + \zeta + \mP_D^{-1}),\qquad
\gradrad = \gradad - Q_{\rm{mag}}\mS.
\end{equation}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\textwidth]{time_evolution.pdf}
\caption{
(Left top panel) Displayed is a trace of the PZ depth ($\delta_{0.5}$) vs.~time, with convective freefall time units on the bottom x-axis and thermal diffusion time units of the background $k$ in the radiative zone on the upper x-axis.
We also display the time evolution of $f$ (Left middle panel, defined in Eqn.~\ref{eqn:f_defn}) and $\xi$ (Left bottom panel, defined in Eqn.~\ref{eqn:xi_defn}).
The vertical lines in the left three panels show when the time trace first converges to within 1\% of its final value, which is denoted by a solid horizontal line.
(Right panel) The vertical profile of $\justgrad/\gradad$ is plotted against height at regular time intervals.
The line color denotes the time, according to the time traces in the left panels.
The constant value of $\gradad$ is denoted by the horizontal dashed grey line, and the value of $\gradrad$ is denoted by the solid grey line.
The location of the Schwarzschild convective boundary is displayed as a vertical dashed black line and denotes the place where $\gradad = \gradrad$.
The top of the penetration zone departure points are plotted over the profile evolution ($\delta_{0.1}$ and $\delta_{0.9}$ as red lines, $\delta_{0.5}$ as black lines).
\label{fig:time_evolution}
}
\end{figure}

@@

The evolution of the other parameters in our theory ($f$, $\xi$) are shown in the middle and bottom left panels of Fig.~\ref{fig:time_evolution}.
We plot the rolling mean, averaged over 1000 freefall time units. 
We see that the values of $f$ and $\xi$ reach their final values ($f \approx 0.67$, $\xi \approx 0.55$) faster than the penetration zone evolves to its full depth.
We quantify this by plotting a vertical line in each of the left three panels which corresponds to the first time in which the time-evolving average converges to within 1\% of the mean final value (calculated over the last 1000 freefall times of the simulation and plotted as a grey horizontal line).

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\textwidth]{vertical_dynamics_panels.pdf}
\caption{
Displayed is an instantaneous snapshot of dynamics in a vertical slice through the simulation with $\mR = 6.4 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$.
In both panels, the nominal Schwarzschild boundary of the convection zone where $\gradad = \gradrad$ is displayed as a dashed horizontal line, and the top of the penetrative zone ($\delta_{0.1}$) is shown by a solid horizontal line.
(Left) The vertical velocity is shown; orange convective upflows extend far past the Schwarzschild boundary of the convection zone but stop abruptly where $\justgrad$ departs from $\gradad$.
(Right) Temperature fluctuations are shown, normalized by their average magnitude at each height in order to clearly display all dynamical features.
Unlike the vertical velocity, $T'$ shows distinctly different behavior in the CZ and PZ, switching sign at the Schwarzschild boundary of the convection zone.
\label{fig:vertical_dynamics_panels}
}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics{parameters_vs_s.pdf}
\caption{
(Left panel) Penetration depths are shown as a function of stiffness for simulations with a discontinuous conductivity.
While the width of the transition layer from the adiabatic PZ to the stable RZ shrinks as a function of $\mS$, the mean penetration depth ($\delta_{0.5}$) is roughly constant.
(Right panel) The width of the thermal transition layer ($\delta_{0.9} - \delta_{0.1}$) is shown as a function of stiffness.
We roughly observe a $\mS^{-1/2}$ scaling, similar to that expected by e.g., \citet{korre_etal_2019}.
\label{fig:parameters_vs_s}
}
\end{figure}

@@

We find a convection zone which extends an additional $X H_p$ beneath the nominal Schwarzschild base of the convection zone.
Past work has suggested from observations that the maximum depth of such an extended adiabatic region should be limited to $0.05 H_p$, which is smaller than what is found in our model \citep[see e.g., section 7.2.1 of][]{basu2016}.
However, our results here are in line with the recent simulations of \citet{kapyla2019}, which suggest an overshooting depth of $0.2 H_p$ at the base of the solar convection zone.
We hope to improve this model and stuff in future work, please hang out with us and make it better.

>>>>

% Preamble
\documentclass[twocolumn]{aastex631}
\usepackage{natbib}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{epstopdf}
\usepackage{hyperref}

@@

\begin{abstract}
Convection is a crucial mechanism for heat transport and dynamical excitation in stars.
Parameterizations like mixing length theory adequately describe bulk convective flows, but the behavior of convective motions near convective boundaries are not well understood.
In this paper we examine how convective motions mix the background thermodynamic profiles and in turn extend the size of the convection zone, a process referred to as convective penetration.
We use a simplified Boussinesq model of stellar convection with a radiative flux.
We derive a ``penetration parameter'' $\mathcal{P}$ which compares how drastically the radiative gradient deviates from the adiabatic gradient on either side of the Schwarzschild convective boundary.
Following \citet{roxburgh1989} and \citet{zahn1991}, we derive a parameterization in which the size of the convection zone is set by $\mP$ and the energy dissipation.
We perform 3D numerical simulations using Dedalus and find good agreement with this theory.
In stellar contexts, we expect $\mathcal{P} \approx 1$ and in this regime our results suggest that convection zones may extend beyond the Schwarzschild boundary by up to $\sim$20-30\% of a mixing length.
We present a MESA solar model which employs our parameterization of convective penetration, and find that the base of the solar convection zone extends by (TODO X amount for some choice of parameters).
We briefly discuss future experiments which could verify and extend these results in more realistic stellar contexts.
\end{abstract}
\keywords{UAT keywords}

@@

The mechanisms referred to as ``convective overshoot'' in the stellar literature fall into two hydrodynamical classes.
The first class is, confusingly, also called ``\emph{convective overshoot}'' in the fluid dynamics literature and refers to motions which extend beyond the convective boundary and mix chemical compositions but importantly do not adjust the thermodynamic profile.
The second class is called ``\emph{convective penetration},'' and refers to convective motions which mix the thermodynamic profiles beyond the convective boundary, thereby extending the adiabatically-mixed convective region.
We will follow a deep history \citep{zahn1991, brummell_etal_2002, korre_etal_2019} and use this terminology; the primary focus of this work is convective penetration.
We are interested in the case where there are no composition gradients, and where the flux driving the convection is constant over long timescales.
We are therefore not focused on the mechanisms by which convection zones grow \citep[e.g., entrainment, ][]{meakin_arnett_2007, viallet_etal_2013, cristini_etal_2017, fuentes_cumming_2020, horst_etal_2021}, but rather the extent of saturated, statistically-stationary convective regions.

@@

\subsection{Kinetic energy \& the dissipation-flux link}
\label{sec:theory_energy}
\begin{figure*}[t!]
\centering
\includegraphics[width=\textwidth]{theory_profiles.pdf}
\caption{
(left) The vertical profile of the horizontally-averaged kinetic energy fluxes $\bar{\mathcal{F}}$ realized in a simulation. 
$\bar{\mathcal{F}}$ is zero at the bottom boundary, the top of the penetrative region (marked by a solid line) and again at the mid-convection zone (marked by a dashed line).
Eqn.~\ref{eqn:integral_constraint} must hold true over an integral between any two of these zeros.
(middle) Measured profiles of $\justgrad$ (green) compared to $\gradad$ (grey, a constant) and $\gradrad$ (red); note the extended penetration zone where $\justgrad \approx \gradad > \gradrad$.
(right) Source terms from Eqn.~\ref{eqn:kinetic_energy_1D} normalized by the maximum of $\overline{\mathcal{B}}$ ($\bar{\mathcal{F}}$ in the left panel is normalized in the same manner).
\label{fig:theory_profiles}
}
\end{figure*}

@@

We now find it instructive to break up the convecting region into a classical ``convection zone'' (CZ) and a extended ``penetration zone'' (PZ); we will assume that convective motions are efficient in each of these zones so that $\justgrad = \gradad$ in both the CZ and PZ.
We furthermore note that the buoyant energy generation is directly proportional to the convective flux, $\bar{\mathcal{B}} = |\alpha|g\bar{w T'} = |\alpha| g \bar{\Fconv}$.
Thus, in the PZ where $\gradad > \gradrad$, we know that $\bar{\Fconv} < 0$ and so $\bar{\mathcal{B}} < 0$ too (see the discussion around Eqn.~\ref{eqn:gradrad_definition}).
Breaking up Eqn.~\ref{eqn:integral_constraint}, we see that
\begin{equation}
%\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz \qquad=\qquad
\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz \,\,=\,\,
\int_{\rm{CZ}} \bar{\Phi}\,dz + \int_{\rm{PZ}} \bar{\Phi}\,dz + \int_{\rm{PZ}}(-\bar{\mathcal{B}})\,dz.
\label{eqn:constraint_cz_pz_split}
\end{equation}
Eqn.~\ref{eqn:constraint_cz_pz_split} is thus arranged so that the (positive) buoyant engine of convection is on the left-hand side, and the (positive) sinks of work are on the RHS.
We see that the size of the PZ is set by some combination of viscous dissipation and buoyancy breaking.
We now parameterize the fraction of the buoyant engine consumed by CZ dissipation  
\begin{equation}
f \equiv \frac{\int_{\rm{CZ}} \bar{\Phi}\,dz}{\int_{\rm{CZ}}\bar{\mathcal{B}}\,dz}.
\label{eqn:f_defn}
\end{equation}
Under this parameterization, Eqn.~\ref{eqn:constraint_cz_pz_split} can be written
\begin{equation}
\frac{\int_{\rm{PZ}} \bar{\Phi}\,dz + \int_{\rm{PZ}}(-\bar{\mathcal{B}})\,dz}{\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz}
= 1 - f,
\label{eqn:first_pz_parameterization}
\end{equation}
and we can immediately read off limits on a hypothetical PZ according to $f$,
\begin{enumerate}
\item In the limit that $f \rightarrow 0$, viscous dissipation is extremely inefficient.
It is probably also reasonable to assume that $\int_{\rm{PZ}}\bar{\Phi}\,dz \rightarrow 0$, and so Eqn.~\ref{eqn:first_pz_parameterization} states that the PZ must be large enough for its negative buoyant work to be equal in magnitude to the positive buoyant work of the CZ.
This is the integral constraint on the maximum size of the PZ that \citet{roxburgh1989} derived.
\item In the limit that $f \rightarrow 1$, viscous dissipation is efficient in the CZ and cancels out the work done by buoyancy.
This is the case in standard Rayleigh-B\'{e}nard convection when the convection is contained between two hard plates.
Per Eqn.~\ref{eqn:first_pz_parameterization}, the positive-definite PZ terms must approach zero and no PZ develops in this limit.
\end{enumerate}
In general, we anticipate from the results of e.g., \citet{currie_browning_2017} that $f$ is closer to 1 than 0, but its precise value must be measured directly from simulations.
Indeed, we find that $f \gg 0$ but $f < 1$ in our simulations (see e.g., Fig.~\ref{fig:theory_profiles}, right panel).

Assuming that a PZ of depth $\delp$ develops above a CZ of depth $L_{\rm{CZ}}$, we model the PZ dissipation as
\begin{equation}
\int_{\rm{PZ}} \bar{\Phi}\,dz = \xi\frac{\delp}{L_{\rm{CZ}}}\int_{\rm{CZ}}\bar{\Phi}\,dz = \xi \delp \Phi_{\rm{CZ}}.
\label{eqn:xi_defn}
\end{equation}
Here $\Phi_{\rm{CZ}}$ is the volume-averaged dissipation value in the CZ and $\xi$ is a parameter that describes the shape of the dissipation profile as a function of height in the PZ.
In other words, we assume that $\bar{\Phi} \approx \Phi_{\rm{CZ}}$ at the CZ-PZ boundary and then falls off with height.
The shape of $\bar{\Phi}$ determines the value of $\xi$, with a linear falloff producing $\xi = 1/2$, a quadratic falloff producing $\xi = 2/3$, and if $\bar{\Phi}$ does not decline with height then $\xi = 1$.
Regardless, $\xi$ is another measurable parameter bounded by $[0, 1]$. 
With this parameterization, we rewrite Eqn.~\ref{eqn:first_pz_parameterization}
\begin{equation}
-\frac{\int_{\rm{PZ}}\bar{\Fconv}\,dz}{\int_{\rm{CZ}}\bar{\Fconv}\,dz} + f\xi\frac{\delp}{L_{\rm{CZ}}}
= (1 - f).
\label{eqn:theory_fraction}
\end{equation}
In order to derive a specific prediction for the PZ depth, it is necessary to specify the vertical shape of $\overline{\Fconv}$.
We will study two cases in this work, laid out below.
In both of these cases, we will define a nondimensional ``Penetration Parameter'' whose magnitude is set by the ratio of the convective flux some equidistant length $\epsilon$ both above and below the Schwarzschild convective boundary $L_s$ (assuming the region above the boundary is an adiabatic penetrative zone),
\begin{equation}
\mP \equiv -\frac{\overline{\Fconv}(z = L_s - \epsilon)}{\overline{\Fconv}(z = L_s + \epsilon)}.
\label{eqn:theory_P_defn}
\end{equation}
Since $\Fconv < 0$ in the PZ, the sign of $\mP$ is positive.
Intuitively, $\mP$ describes which terms are important in Eqn.~\ref{eqn:first_pz_parameterization}.
When $\mP \ll 1$, the buoyancy term dominates in the PZ and dissipation can be neglected there.
When $\mP \gg 1$, buoyancy is negligible in the PZ and dissipation constrains the size of the PZ.
When $\mP \sim 1$, both terms matter.

@@

\section{Simulation Details}
We nondimensionalize Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq} on the length scale of the Schwarzschild-unstable convection zone $L_s$, the timescale of freefall across that convection zone $\tau_{\rm{ff}}$, and the temperature scale of the internal heating over that freefall time $\Delta T$,
\begin{equation}
\begin{split}
&T^* = (\Delta T)T = Q_0 \tau_{\rm{ff}} T,\qquad
Q^* = Q_0 Q,
\\
&\partial_{t^*} = \tau_{\rm{ff}}^{-1}\partial_t = \left(\frac{|\alpha| g Q_0}{L_s}\right)^{1/3} \partial_t,\,\,\,\,\,
\grad^* = L_s^{-1} \grad,
\\
&\vec{u}^* = u_{\rm{ff}}\vec{u} = \left(|\alpha| g Q_0 L_s^2\right)^{1/3}\vec{u},\qquad
p^* = \rho_0 u_{\rm{ff}}^2\varpi,
\\
&k^* = (L_s^2 \tau_{\rm{ff}}^{-1})k,\qquad
\mR = \frac{u_{\rm{ff}} L_s}{\nu},\qquad
\Pran = \frac{\nu}{\chi}.
\end{split}
\end{equation}
For convenience, here we define quantities with $*$ (e.g., $T^*$) as being the ``dimensionful'' quantities of Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq}.
Going forward, quantities without $*$ (e.g., $T$) will be dimensionless.
The dimensionless equations of motion are therefore
\label{sec:simulation_details}
\begin{align}
&\grad\dot\vec{u} = 0 
\label{eqn:nondim_incompressible} \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\grad \varpi + T \hat{z} + \mR^{-1}\grad^2 \vec{u}
\label{eqn:nondim_momentum} \\
\begin{split}
\partial_t T + \vec{u}\dot\grad T + w \grad_{\rm{ad}}  + \grad\dot[-k \grad \overline{T}]\qquad\qquad 
\\
\qquad\qquad\qquad\qquad\qquad= (\Pran\mR)^{-1}\grad^2 T' + Q.
\label{eqn:nondim_temperature}
\end{split}
\end{align}
We construct a domain in the range $z \in [0, L_z]$ where in this work we choose $L_z \geq 2$ so that the domain is at least twice as deep as the Schwarzschild-unstable convection zone.
We decompose the temperature field into a time-stationary initial background and fluctuations, $T(x, y, z, t) = T_0(z) + T_1(x, y, z, t)$.
For boundary conditions, we impose impenetrable, no-slip boundary conditions at the top and bottom of the box so that $\vec{u} = 0$ at $z = [0, L_z]$.
We also impose a fixed-flux boundary at the bottom of the box ($\partial_z T_1 = 0$ at $z = 0$) and a fixed temperature boundary at the top of the domain ($T_1 = 0$ at $z = L_z$).
For a select few simulations, we impose stress-free instead of no-slip boundary conditions ($w = 0$ and $\partial_z u = \partial_z v = 0$ at $z = [0, L_z]$).

@@

\subsection{Case I: Discontinuous flux}
Most of the simulations in this paper have a discontinuous convective flux at the Schwarzschild convective boundary.
We achieve this by constructing a discontinuous radiative conductivity,
\begin{equation}
k = \begin{cases}
k_{\rm{CZ}}	&	z < 1 \\
k_{\rm{RZ}} &	z \geq 1
\end{cases},
\label{eqn:sim_discontinuous_k}
\end{equation}
where CZ refers to the convection zone and RZ refers to the radiative zone (some of which will be occupied by the penetrative zone PZ).
Leaving $\mS$ and $\mP_D$ as free parameters and requiring that the adiabatic gradient can carry $\Fbot$ at $z = 0$ and that the radiative gradient can carry $F_H + \Fbot$ for $z \geq 1$ specifies this system fully,
\begin{equation}
\begin{split}
k_{\rm{RZ}} = \frac{\delta_H}{\mS\mP_D},\\
k_{\rm{CZ}} = k_{\rm{RZ}}\frac{1}{1 + \zeta + \mP_D^{-1}},\\
\gradad = Q_{\rm{mag}}\mS\mP_D(1 + \zeta + \mP_D^{-1}),\\
\gradrad = \gradad - Q_{\rm{mag}}\mS.
\end{split}
\end{equation}

@@

\begin{figure*}[t!]
\centering
\includegraphics[width=\textwidth]{time_evolution.pdf}
\caption{
(Left top panel) Displayed is a trace of the PZ depth ($\delta_{0.5}$) vs.~time, with convective freefall time units on the bottom x-axis and thermal diffusion time units of the background $k$ in the radiative zone on the upper x-axis.
We also display the time evolution of $f$ (Left middle panel, defined in Eqn.~\ref{eqn:f_defn}) and $\xi$ (Left bottom panel, defined in Eqn.~\ref{eqn:xi_defn}).
The vertical lines in the left three panels show when the time trace first converges to within 1\% of its final value, which is denoted by a solid horizontal line.
(Right panel) The vertical profile of $\justgrad/\gradad$ is plotted against height at regular time intervals.
The line color denotes the time, according to the time traces in the left panels.
The constant value of $\gradad$ is denoted by the horizontal dashed grey line, and the value of $\gradrad$ is denoted by the solid grey line.
The location of the Schwarzschild convective boundary is displayed as a vertical dashed black line and denotes the place where $\gradad = \gradrad$.
The top of the penetration zone departure points are plotted over the profile evolution ($\delta_{0.1}$ and $\delta_{0.9}$ as red lines, $\delta_{0.5}$ as black lines).
\label{fig:time_evolution}
}
\end{figure*}

@@

The evolution of the other parameters in our theory ($f$, $\xi$) are shown in the middle and bottom left panels of Fig.~\ref{fig:time_evolution}.
We plot the rolling mean, averaged over 200 freefall time units. 
We see that the values of $f$ and $\xi$ reach their final values ($f \approx 0.67$, $\xi \approx 0.55$) faster than the penetration zone evolves to its full depth.
We quantify this fast evolution by plotting a vertical line in each of the left three panels corresponding to the first time at which the rolling average converges to within 1\% of its final value (averaged over the final 1000 freefall times of the simulation and plotted as a grey horizontal line).
The evolved values of $f$ and $\xi$ indicate that roughly 2/3 of the buoyancy work is dissipated in the bulk CZ, so that 1/3 is available for PZ dissipation, and the shape of dissipation in the PZ is slightly steeper than linear.

@@

\begin{figure*}[t!]
\centering
\includegraphics[width=\textwidth]{vertical_dynamics_panels.pdf}
\caption{
Displayed is an instantaneous snapshot of dynamics in a vertical slice through the simulation with $\mR = 6.4 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$.
In both panels, the nominal Schwarzschild boundary of the convection zone where $\gradad = \gradrad$ is displayed as a dashed horizontal line, and the top of the penetrative zone ($\delta_{0.1}$) is shown by a solid horizontal line.
(Left) The vertical velocity is shown; orange convective upflows extend far past the Schwarzschild boundary of the convection zone but stop abruptly where $\justgrad$ departs from $\gradad$.
(Right) Temperature fluctuations are shown, normalized by their average magnitude at each height in order to clearly display all dynamical features.
Unlike the vertical velocity, $T'$ shows distinctly different behavior in the CZ and PZ, switching sign at the Schwarzschild boundary of the convection zone.
\label{fig:vertical_dynamics_panels}
}
\end{figure*}

@@

\begin{figure*}[t!]
\centering
\includegraphics{parameters_vs_s.pdf}
\caption{
(Left panel) Penetration depths are shown as a function of stiffness for simulations with a discontinuous conductivity.
While the width of the transition layer from the adiabatic PZ to the stable RZ shrinks as a function of $\mS$, the mean penetration depth ($\delta_{0.5}$) is roughly constant.
(Right panel) The width of the thermal transition layer ($\delta_{0.9} - \delta_{0.1}$) is shown as a function of stiffness.
We roughly observe a $\mS^{-1/2}$ scaling, similar to that expected by e.g., \citet{korre_etal_2019}.
\label{fig:parameters_vs_s}
}
\end{figure*}

@@

We find a convection zone which extends an additional $X H_p$ beneath the nominal Schwarzschild base of the convection zone.
Past work has suggested from observations that the maximum depth of such an extended adiabatic region should be limited to $0.05 H_p$, which compares to our model in X way \citep[see e.g., section 7.2.1 of][]{basu2016}.
However, the recent simulations of \citet{kapyla2019} suggest an overshooting depth of $0.2 H_p$ at the base of the solar convection zone.
We hope to improve this model and stuff in future work, please hang out with us and make it better.
